### 2014-10-28 LongDataResearchNotes/ARModel.Rmd
Several itterations of the model but nothing that is satisfactory.  Will continue with specification

LagFormData<-sqldf("select  LongWtrends.DateOnly, LongWtrends.hour, LongWtrends.F, LongWtrends.HE, CopyLong.F as LagF, CopyLong.HE as LagHE, LongWtrends.Weather, CopyLong.Weather as LagWeather  from LongWtrends,CopyLong where LongWtrends.DateOnly=(CopyLong.DateOnly-7) and LongWtrends.hour=CopyLong.hour;   ")

@@

summary(gls(HE~hour+(F+LagHE+Weather+LagWeather):hour, data=LagFormData,corAR1(form=~1),na.action=na.omit))
```
Sweet works except hours 1-5

@@

```{r}
LagFormData<-sqldf("select * from LagFormData order by DateOnly,hour;")
summary(gls(HE~hour+(F+LagHE+Weather+LagWeather):hour, data=LagFormData,corAR1(form=~1),na.action=na.omit))
```

and the results are different.  Now we have to figure out which is right, or perhaps both.

>>>>

LagFormData<-sqldf("select  LongWtrends.DateOnly, LongWtrends.hour, LongWtrends.F, LongWtrends.HE, CopyLong.F as LagF, CopyLong.HE as LagHE, LongWtrends.Weather, CopyLong.Weather as LagWeather  from LongWtrends,CopyLong where LongWtrends.DateOnly=(CopyLong.DateOnly+7) and LongWtrends.hour=CopyLong.hour;   ")

@@

summary(gls(HE~hour+(F+LagHE+Weather+LagWeather):hour, data=LagFormData,corAR1(form=~1),na.action=na.omit))$tTable
```
Sweet works except hours 1-5

@@

```{r}
LagFormData<-sqldf("select * from LagFormData order by DateOnly,hour;")
ARbyHour<-gls(HE~hour+(F+LagHE+Weather+LagWeather):hour, data=LagFormData,corAR1(form=~1),na.action=na.omit)
summary(ARbyHour)$tTable
```

and the results are different.  Now we have to figure out which is right, or perhaps both.  The likelyhood suggests hour within day, i.e., the worse one.

Lets get into the day of week effects and see if it is still there.  There was a Monday and Tuesday problem

```{r}
LagFormData$DOW<-as.factor(weekdays(LagFormData$DateOnly))
LagFormData$DayType<-"MidWeek"
LagFormData$DayType[LagFormData$DOW=="Monday"| LagFormData$DOW=="Tuesday"]<-"EarlyWeek"
LagFormData$DayType[LagFormData$DOW=="Saturday"| LagFormData$DOW=="Sunday"]<-"Weekend"
LagFormData$DayType<-as.factor(LagFormData$DayType)
summary(LagFormData)

LagFormData<-sqldf("select * from LagFormData order by DateOnly,hour;")
ARbyHourDay<-gls(HE~-1+(hour+(F+LagHE+Weather+LagWeather):hour):DayType, data=LagFormData,corAR1(form=~1),na.action=na.omit)
summary(ARbyHourDay)$tTable
# 
# ARbyHourDay<-gls(HE~(hour+(F+LagHE+Weather+LagWeather):hour):weekdays(DateOnly), data=LagFormData,corAR1(form=~1),na.action=na.omit)
# summary(ARbyHourDay)$tTable
```

Try without lag of forecast

```{r}

LagFormData<-sqldf("select * from LagFormData order by DateOnly,hour;")
ARbyHourDayNoLagLoad<-gls(HE~-1+(hour+(F+Weather+LagWeather):hour):DayType, data=LagFormData,corAR1(form=~1),na.action=na.omit)
summary(ARbyHourDayNoLagLoad)$tTable

We think that lag of actual is in the forecast.

No lag of actual but with lag forecast

```{r}

LagFormData<-sqldf("select * from LagFormData order by DateOnly,hour;")
ARbyHourDayLagF<-gls(HE~-1+(hour+(F+Weather+LagWeather+LagF):hour):DayType, data=LagFormData,corAR1(form=~1),na.action=na.omit)
summary(ARbyHourDayLagF)$tTable
